Tampering Detection In Low-Power Smart Cameras

### 2015-05-26 paper.tex

@@

The algorithm uses low computational techniques: the biggest effort is made by computation of the feature $g(t)$, which needs $34$ operations per pixel, due to the Sobel filter used during the convolution.
The computational load could decrease using Fast Fourier Transform (FFT) \cite{brigham1988fast} and operating in the frequency domain.

>>>>

\begin{equation}
\label{eq:lumaRegions}
\begin{array}{ccc}
l^k(t)&  = & \mathcal{L}^k[z_t] = \frac{\sum_{R_k} z_t(x) }{|{R_k}|}\\
\partial l^k(t) & =& l^k(t)-l^k(t-1) 
\end{array},
\end{equation}

%\begin{equation}
%\label{eq:energyLuma}
%l(t) = \mathcal{L}[z_t] =\frac{\sum_{\mathcal{X}} z_t(x) }{|\mathcal{X}|} ,
%\end{equation}  
%
%
%\begin{equation}
%\label{eq:gradientDetr}
%\frac{\partial g}{\partial t}(t) = g(t) - g(t-1),
%\end{equation}
%
%
%\begin{equation}
%\label{eq:lumaDetr}
%\frac{\partial l}{\partial t}(t) = l(t) - l(t-1).
%\end{equation}

\subsection{Outlier Detection}\label{subsec:MonitoringScheme}

\begin{equation}
\label{eq:soglieGradiente}
\begin{array}{lcl}
\Gamma_{min}^k & = & \hat{\mu}_g^k -\gamma \hat{\sigma}_g^k\\
\Gamma_{max}^k & = & \hat{\mu}_g^k + \gamma \hat{\sigma}_g^k
\end{array},
\end{equation}
dove $\hat{\mu}_g^k$ indica il valore medio delle osservazioni del training set
\begin{equation}
\hat{\mu}_g^k = \frac{\sum_{\tau = 1}^{T_{o}} \frac{\partial g^k}{\partial t}(\tau)}{T_{o}}, \nonumber
\end{equation}
$\hat{\sigma}_g^k$ indica la deviazione standard delle osservazioni del training set
\begin{equation}
\hat{\sigma}_g^k  = \sqrt{\frac{1}{T_{o}-1}\sum_{\tau=1}^{T_{o}}\left(\frac{\partial g^k}{\partial t}(\tau) - \hat{\mu}_g^k(\tau)\right)^2} \nonumber
\end{equation}
e $\gamma>1$ \`e un parametro moltiplicativo ottenuto sperimentalmente.\\

\begin{equation}
\label{eq:soglieLuma}
\begin{array}{rcl}
\Gamma_{min}^k & = & \hat{\mu}_l^k -\gamma \hat{\sigma}_l^k\\
\Gamma_{max}^k & = & \hat{\mu}_l^k + \gamma \hat{\sigma}_l^k
\end{array},
\end{equation}
dove $\hat{\mu}_l^k$ indica il valore medio delle osservazioni del training set
\begin{equation}
\hat{\mu}_l^k = \frac{\sum_{\tau = 1}^{T_{o}} \frac{\partial l^k}{\partial t}(\tau)}{T_{o}}, \nonumber
\end{equation}
$\hat{\sigma}_l^k$ indica la deviazione standard delle osservazioni del training set
\begin{equation}
\hat{\sigma}_l^k  = \sqrt{\frac{1}{T_{o}-1}\sum_{\tau=1}^{T_{o}}\left(\frac{\partial l^k}{\partial t}(\tau) - \hat{\mu}_l^k(\tau)\right)^2} \nonumber
\end{equation}
e $\gamma>1$ \`e un parametro moltiplicativo ottenuto sperimentalmente.\\

\subsection{Algorithm Summary}\label{subsec:AlgorithmSummary}

%\begin{algorithm}[tp]
%	% \SetAlgoNoLine
%	\LinesNumbered
%	\SetAlgoNlRelativeSize{0}
%	\SetNlSty{small}{}{.}
%	\textbf{Configuration}:\\
%	\lnl{DEF-Tr0} Extract regions $\{R_k\}, k=1,\dots,K$  \\
%	\lnl{DEF-Tr1} \For{$t=1,\dots,T_{o}$}
%	{	\lnl{DEF-Tr2} Acquire frame $z_t$ \\
%		\lnl{DEF-Tr2a} \For{$k=1,\dots,K$}{
%			\lnl{DEF-Tr3a} Compute $g^k(t)$, $\frac{\partial g^k}{\partial t}(t)$ for the region $R_k$\\
%		}
%		\lnl{DEF-Tr3} Compute $g(t)$, $\frac{\partial g}{\partial t}(t)$ \\
%	}
%	\lnl{DEF-Tr6a} \For{$k=1,\dots,K$}{
%		\lnl{DEF-Tr7a} Define thresholds $\Gamma_{min}^k$ and $\Gamma_{max}^k$\\
%	}
%	\lnl{DEF-Tr5} Define CDT parameters on $g(t)$ variance\\
%	\textbf{Operational phase}:\\
%	\lnl{DEF-Test1} \For{$t=T_{o},\dots,\infty$}{
%		\lnl{DEF-Test2} Acquire frame $z_t$ \\
%		\lnl{DEF-Tr3b} Compute $g(t)$, $\frac{\partial g}{\partial t}(t)$ \\
%		\lnl{DEF-Test2a} $n=0$\\
%		\lnl{DEF-Test4a} \For{$k=1,\dots,K$}{
%			\lnl{DEF-Test5a} Compute $g^k(t)$, $\frac{\partial g^k}{\partial t}(t)$ for the region $R_k$\\
%			\lnl{DEF-Test6a} \If{$\frac{\partial g^k}{\partial t}(t) < \Gamma_{min}^k \vee \frac{\partial g^k}{\partial t}(t) > \Gamma_{max}^k $}{
%				\lnl{DEF-Test7a} $n=n+1$\\
%			}
%		}
%		\lnl{DEF-Test81} \If{$n \geq K-1$}{
%			\lnl{DEF-Test91} $z_t$ is a defocused frame\\
%		}
%		\lnl{DEF-Test8} \If{CDT detect a change on $g(t)$ variance}{
%			\lnl{DEF-Test9} $z_t$ is a defocused frame\\
%		}
%	}   
%	\caption{Blur detection algorithm}
%	\label{alg:DEFOCUS}
%\end{algorithm}

%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

@@

The algorithm uses low computational techniques: the biggest effort is made by computation of the feature $g(t)$, which needs $34$ operations per pixel, due to the Sobel filter used during the convolution.
